\documentclass[12pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{margin=2.5cm}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{float}
\usepackage{caption}
\usepackage{CJKutf8}

\lstset{
  basicstyle=\ttfamily\small,
  breaklines=true,
  frame=single,
  backgroundcolor=\color{gray!10},
  xleftmargin=1em,
  framexleftmargin=0.5em,
}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue,
}

\title{\textbf{Few-Shot Tactical Strategy Recognition in Badminton} \\[0.5em]
\large Using Self-Supervised Skeleton-Based Spatio-Temporal Graph Learning \\[0.5em]
\normalsize Project Report}
\author{[Author Name] \quad | \quad [Institution] \quad | \quad [Date]}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This project develops an end-to-end pipeline for recognizing fine-grained
tactical strategies in badminton from raw match footage. The system extracts
dual-player skeleton sequences from video, learns generalizable spatio-temporal
representations through supervised contrastive pre-training on shot-type labeled
data, and classifies tactical patterns using few-shot prototypical networks
with only 40 expert-labeled rallies. We target five classifiable strategies
(intercept, defensive, move to net, create depth, passive) and investigate
two core research questions: (1) the relative contribution of spatial versus
temporal features to strategy recognition, and (2) the effectiveness of
self-supervised pre-training in reducing label dependency. Pre-training uses
20 ShuttleSet matches ($\sim$17,000 shots) with shot-type supervision via SupCon
(Supervised Contrastive Learning); few-shot classification is evaluated on
the held-out FineBadminton set. The system additionally outputs shot-type
predictions alongside strategy at inference.
\end{abstract}

\newpage
\tableofcontents
\newpage

%----------------------------------------------------------------------
\section{Introduction}
%----------------------------------------------------------------------

Tactical analysis in badminton remains a manually intensive process. Coaches
review match footage frame-by-frame to identify strategic patterns such as
interceptions, defensive formations, and net approaches. This process is
time-prohibitive, subjective, and inaccessible to amateur and
semi-professional players who lack dedicated analyst support.

Automated approaches face a fundamental bottleneck: fine-grained tactical
annotations require domain expertise and are expensive to produce at scale. In
badminton, a hitting player's strategy is reactive and anticipatory --- it is
influenced not only by their own intentions but also by the opponent's
positioning, movement, and state. The FineBadminton dataset, the only
publicly available resource with expert-level strategy labels, contains just
40 annotated rallies. Fully supervised deep learning is infeasible at this
scale.

We target five classifiable strategies that are distinguishable from skeleton
and positional data alone: \textbf{intercept}, \textbf{defensive}, \textbf{move to net},
\textbf{create depth}, and \textbf{passive}. Table~\ref{tab:strategies} defines each strategy
and the observable signals that distinguish it.

\begin{table}[H]
\centering
\caption{Target strategy definitions and observable skeleton/position signals}
\label{tab:strategies}
\small
\begin{tabularx}{\textwidth}{lXXXX}
\toprule
\textbf{Strategy} & \textbf{Goal} & \textbf{Hitter Signals} & \textbf{Opponent Signals} & \textbf{Shot Type} \\
\midrule
\textbf{Intercept} & Cut off shuttle early; offensive play & Early racket contact; forward court position; fast forward step & Opponent mid-court/forward; low lateral movement; upright pose & Flat / aggressive \\
\textbf{Defensive} & Protect position; recover control & Reactive contact; rear-court position; stretched body & Opponent forward/stretched; off-balance; weight leaning forward/back & High lift / clear / block \\
\textbf{Move to Net} & Drive / drop / approach & Sequential forward steps; forward racket motion & Opponent gradually moving backward; mid-court; upright stance & Advance toward net; offensive positioning \\
\textbf{Create Depth} & Deep clear / push back opponent & Rear-court contact; shot directed deep; forward/backward step & Opponent mid/front court; moving forward; leaning slightly forward & Push opponent to rear court; gain spatial control \\
\textbf{Passive} & Recovery play; minimal gain & Neutral placement; low speed; minimal forward/backward movement & Opponent mid/rear court; stable stance; minimal movement & Any non-aggressive / neutral shot \\
\bottomrule
\end{tabularx}
\end{table}

\textbf{Out of scope:} Deception (requires biomechanical discrepancy data between
preparation and execution phases --- not captured in 2D skeletons), hesitation
(requires sub-frame timing analysis beyond our temporal resolution), seamlessly
(a quality modifier, not a discrete strategy class), and ``a high net early
shot'' (insufficient samples for reliable classification). Shots with these
labels are excluded from the training set.

\textbf{Research questions:}
\begin{itemize}
  \item \textbf{RQ1:} What is the relative contribution of spatial features (player
    positioning, court geometry) versus temporal features (movement sequences,
    timing patterns) to the recognition of different tactical strategies?
  \item \textbf{RQ2:} To what extent does self-supervised contrastive pre-training on
    unlabeled match footage improve few-shot tactical classification compared
    to randomly initialized baselines?
\end{itemize}

%----------------------------------------------------------------------
\section{Literature Review}
%----------------------------------------------------------------------

\subsection{Skeleton-Based Action Recognition}

Skeleton-based approaches model human motion as sequences of joint coordinates
rather than raw pixel data. ST-GCN \cite{yan2018} introduced graph
convolutions over spatial joint connections and temporal sequences, achieving
81.5\% top-1 accuracy on Kinetics-400 for general action recognition. Subsequent
work (2s-AGCN, MS-G3D, CTR-GCN) improved spatial attention mechanisms and
multi-scale temporal modeling. However, these methods target coarse action
categories (e.g., ``playing badminton'' vs. ``playing tennis'') rather than
fine-grained tactical patterns within a single sport.

\subsection{Self-Supervised Learning for Skeleton Sequences}

Label-free representation learning for skeletons has advanced rapidly.
CrosSCLR \cite{li2021} introduced cross-view contrastive learning across
different skeleton augmentation views. AimCLR \cite{guo2022} addressed
augmentation sensitivity through extreme augmentation strategies. 3s-HCN
applied hierarchical contrastive learning at joint, body-part, and sequence
levels. These methods demonstrate that skeleton embeddings pre-trained without
labels can match or approach supervised performance when fine-tuned, motivating
our self-supervised pre-training strategy.

\subsection{Badminton Analytics}

Existing computational badminton analysis focuses primarily on shot-level
classification rather than strategic reasoning. CoachAI \cite{wang2022} applied ShuttleNet (ResNet+LSTM) to classify 22 shot types on the ShuttleSet
dataset, achieving 73.4\% accuracy. FineBadminton contributed fine-grained
annotations including strategy labels but did not report classification results
for tactical categories --- its contribution was the annotation framework itself.

Most recently, BST \cite{chang2025} (CVPR 2025 Workshop) introduced a
Transformer-based approach for skeleton-based stroke classification on
ShuttleSet, using both player skeleton sequences and shuttlecock trajectory as
inputs. BST outperforms previous methods on stroke type classification (smash,
clear, drop, etc.), establishing the current state-of-the-art for
skeleton-based badminton analysis. Concurrently, RacketVision \cite{dong2025} advanced racket detection and tracking in badminton video, providing a
complementary signal for fine-grained action understanding.

Critically, BST and RacketVision operate at the stroke type level --- they
classify \emph{what} shot was played, not \emph{why} it was played. No published work
addresses automated tactical strategy classification in badminton.

\subsection{Few-Shot and Meta-Learning in Sports}

Prototypical Networks \cite{snell2017} remain a strong baseline for
few-shot classification, learning a metric space where classification is
performed by distance to class prototypes. Applications in sports have been
limited: few-shot methods have been explored for player identification and rare
event detection, but not for tactical pattern recognition. The scarcity of
tactical labels makes this an ideal application domain.

\subsection{Research Gap}

\begin{table}[H]
\centering
\caption{Positioning relative to existing work}
\label{tab:research-gap}
\small
\begin{tabular}{llll}
\toprule
\textbf{Method} & \textbf{Task} & \textbf{Data Regime} & \textbf{Tactical?} \\
\midrule
CoachAI ShuttleNet & Shot type (22-cls) & Fully supervised & No \\
BST (Chang, 2025) & Stroke type classification & Fully supervised (skeleton + trajectory) & No \\
RacketVision (Dong, 2025) & Racket detection & Fully supervised & No \\
ST-GCN & General action recognition & Fully supervised & No \\
CrosSCLR / AimCLR & Action recognition & Self-supervised & No \\
Prototypical Networks & Image classification & Few-shot & No \\
\textbf{Ours (proposed)} & \textbf{Tactical strategy} & \textbf{SSL + few-shot} & \textbf{Yes} \\
\bottomrule
\end{tabular}
\end{table}

%----------------------------------------------------------------------
\section{Proposed Solution}
%----------------------------------------------------------------------

We propose a three-stage pipeline:

\begin{enumerate}
  \item \textbf{Skeleton extraction} from raw video using GDINO-guided YOLOv8-Pose,
    with spatial court-region masking to eliminate non-player detections
    (chair umpires, ball kids), producing dual-player joint sequences.
  \item \textbf{Supervised contrastive pre-training (SupCon)} on 20 ShuttleSet matches
    (15 train / 5 validation) using shot-type labels. Positive pairs are shots
    of the same type; negative pairs are shots of different types. This forces
    the encoder to learn shot mechanics rather than player identity, and
    provides richer supervisory signal than self-supervised SimCLR alone.
  \item \textbf{Few-shot strategy classification} using prototypical networks on the
    small FineBadminton labeled set (30 train rallies / 10 test rallies).
  \item \textbf{Dual inference output:} strategy prediction (5 classes, confidence +
    margin) and shot-type prediction (17 classes, logistic head trained on
    frozen encoder) --- enabling expert cross-validation of high-confidence
    strategy predictions.
\end{enumerate}

The approach is skeleton-based rather than pixel-based, providing
interpretability and robustness to visual variation (camera angle, lighting,
jersey color). Skeleton inputs also align directly with the strategy taxonomy:
all five target strategies are defined in terms of joint positions, velocities,
and inter-player geometry --- precisely what the skeleton graph captures.

\subsection{Architecture Overview}

\begin{lstlisting}[basicstyle=\ttfamily\footnotesize]
 PHASE A -- SSL PRE-TRAINING  (ShuttleSet, ~17,000 shots, no strategy labels)

  Rally video frames
        |
        v
  YOLOv8 / GDINO --> skeleton.npy  (2, T, 34)   x,y of 34 joints
        |
        v
  Feature Engineering --> L2: position + velocity + court distances  (9, T, 34)
        |
        +---- augment view 1 --> ST-GCN encoder --> projection head --+
        |                                                              +-> SimCLR / SupCon loss
        +---- augment view 2 --> ST-GCN encoder --> projection head --+
                                      |
                                      v
                              ssl_pretrained_L2.pt   <- saved weights


 PHASE B -- FEW-SHOT TRAINING  (FineBadminton, 40 labelled rallies)

  skeleton.npy  (2, T, 34)
        |
        v
  Feature Engineering (L2)  ->  (9, T, 34)
        |
        v
  ST-GCN encoder  <- load ssl_pretrained_L2.pt
        |
        v
  embedding  (256,)
        |
        v
  Prototypical Network
   +-----------------------------------------------------+
   |  support set (k labelled shots per strategy)         |
   |  -> compute class prototype (mean embedding)         |
   |                                                      |
   |  query shot -> nearest prototype -> predicted strategy|
   +-----------------------------------------------------+
        |
        v
  fewshot_L2.pt   <- saved weights + prototypes


 INFERENCE

  New video
        |
        v
  skeleton -> Feature Eng (L2) -> ST-GCN -> embedding (256,)
                                               |
                              +----------------+----------------+
                              v                                  v
                     ProtoNet                          shot_type_clf
                  strategy + confidence              shot type + confidence
             (intercept / defensive /              (smash / drop / clear / ...)
              net / depth / passive)


 ABLATION  -- answers RQ1 and RQ2

  RQ1 -- which input features matter?  (Step 1a, random init, ST-GCN)
  +------------------------------------------+
  |  L0 (x,y only)          -> score         |
  |  L1 (+ velocity)        -> score         |  <- compare
  |  L2 (+ court distances) -> score         |
  |  L3 (+ joint angles)    -> score         |
  +------------------------------------------+

  RQ2 -- does pre-training help?  (Step 3, best layer from RQ1, ST-GCN)
  +------------------------------------------+
  |  Random init            -> score         |
  |  SimCLR (self-supervised) -> score       |  <- compare
  |  SupCon (shot-type labels) -> score      |
  +------------------------------------------+
\end{lstlisting}

%----------------------------------------------------------------------
\section{Datasets \& Data Acquisition}
%----------------------------------------------------------------------

Both datasets feature professional broadcast matches. For the purpose of this
project, we classify tactical strategy \textbf{per shot}. The rally and match
labels are not relevant to the classification task; they appear in the demo UI
for ease of navigation convention.

\textbf{Scoring context.} Under modern BWF rally scoring, each rally gives 1 point
regardless of who served. Up to 177 rallies are possible in a 3-set match;
professional matches typically have 120--150 rallies. Each rally consists of
multiple shots (strokes), each labeled with the hitting player's strategy.

\subsection{FineBadminton --- Labeled Dataset}

FineBadminton is our fine-grained labeled dataset used for few-shot
classification (Phase B).

\textbf{Frame Extraction.} The dataset comes with pre-extracted frames at 20 FPS,
organized by rally ID. No video download is required.

\textbf{Scale.} 40 rallies, 414 annotated shots. After excluding 59 shots with
out-of-scope strategy labels (deception $\times$14, high\_net\_early $\times$36, hesitation $\times$8,
seamlessly $\times$1), we have \textbf{355 shots with strategy labels}, of which \textbf{296 have
successfully extracted skeletons} used in training.

\textbf{Key annotation fields per shot:}

\begin{table}[H]
\centering
\small
\begin{tabular}{ll}
\toprule
\textbf{Field} & \textbf{Description} \\
\midrule
\texttt{hit\_frame} & Exact contact frame (absolute, no missing values) \\
\texttt{start\_frame} / \texttt{end\_frame} & Shot window boundaries \\
\texttt{hitter} & \texttt{"top"} or \texttt{"bottom"} court player \\
\texttt{hit\_type} & Stroke type (12 classes) \\
\texttt{subtype} & Sub-classification (e.g., ``flat lift'', ``short serve'') \\
\texttt{quality} & Annotator quality score 1--7 \\
\texttt{ball\_area} & Court zone of shot (9 zones) \\
\texttt{strategies} & Tactical strategy labels (our classification target) \\
\texttt{shot\_characteristics} & ``cross-court'', ``straight'', ``over head'', etc. \\
\texttt{player\_actions} & ``forehand'', ``backhand'', ``turnaround'' \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Strategy label distribution (N=355 shots, multi-label):}

\begin{table}[H]
\centering
\small
\begin{tabular}{lrr}
\toprule
\textbf{Strategy} & \textbf{Count} & \textbf{\% of shots} \\
\midrule
passive & 137 & 33.1\% \\
intercept & 120 & 29.0\% \\
create depth & 61 & 14.7\% \\
defensive & 61 & 14.7\% \\
move to net & 59 & 14.3\% \\
(excluded: high\_net\_early) & 44 & --- \\
(excluded: hesitation) & 27 & --- \\
(excluded: deception) & 21 & --- \\
(excluded: seamlessly) & 25 & --- \\
\bottomrule
\end{tabular}
\end{table}

Note: \texttt{move\_to\_net} has only 18 samples after windowing and skeleton extraction
(6.1\% of training set) --- this is the most data-scarce class and underperforms
accordingly in baseline experiments (see \S\ref{sec:results}).

\subsection{ShuttleSet --- SSL Pre-Training Dataset}

ShuttleSet is our large-scale dataset used for supervised contrastive
pre-training (Phase A). Unlike FineBadminton, it carries \textbf{shot-type labels}
(19 classes) but no tactical strategy labels.

\textbf{Frame Extraction.} The dataset provides CSV annotations and YouTube video
links only. We downloaded videos via yt-dlp and extracted frames using a
streaming pipeline (frame stride = 4, every 4th frame extracted + all annotated
hit frames). Of 44 matches in \texttt{match.csv}: 38 are usable broadcast-angle
matches. \textbf{20 matches were selected for skeleton extraction} due to Colab GPU
time constraints. 4 matches were excluded earlier due to non-standard broadcast
camera angles (close-up or side-on views).

\textbf{Scale (20 matches, estimated):}

\begin{table}[H]
\centering
\small
\begin{tabular}{lr}
\toprule
\textbf{Statistic} & \textbf{Value} \\
\midrule
Matches extracted & 20 (of 38 usable) \\
Total stroke records & $\sim$17,000 (est.) \\
Total rallies & $\sim$590 (est.) \\
Unique shot types & 17 (unified vocabulary) \\
Avg strokes per match & $\sim$847 \\
\bottomrule
\end{tabular}
\end{table}

\emph{Exact figures updated after extraction completes.}

\textbf{Train/Validation split (match-level):}

\begin{table}[H]
\centering
\small
\begin{tabular}{lrrl}
\toprule
\textbf{Split} & \textbf{Matches} & \textbf{Strokes (est.)} & \textbf{Role} \\
\midrule
Train & 15 & $\sim$12,700 & SupCon pre-training \\
Validation & 5 & $\sim$4,200 & Shot-type linear probe (proxy metric) \\
\textbf{Total} & \textbf{20} & $\sim$\textbf{17,000} & --- \\
\bottomrule
\end{tabular}
\end{table}

Split at match level to prevent frame leakage, with greedy balancing to
minimise KL divergence between train and validation shot-type distributions.

\textbf{Validation role:} The 5 held-out matches are used to evaluate
shot-type classification accuracy as a proxy for representation quality ---
if the encoder separates shot types well, it likely separates strategies too.
The same encoder is then loaded for expert-verified strategy evaluation on
selected SS validation shots (qualitative; see Section~\ref{sec:expert-eval}).

\textbf{Key annotation fields (from per-match CSV files):}

\begin{table}[H]
\centering
\small
\begin{tabular}{ll}
\toprule
\textbf{Field} & \textbf{Description} \\
\midrule
\texttt{frame\_num} & Absolute frame index of the hit event \\
\texttt{type} & Shot type label (19 classes, Chinese) \\
\texttt{player} & \texttt{"A"} or \texttt{"B"} \\
\texttt{player\_location\_x/y} & Hitter pixel position (used for hitter-first ordering) \\
\texttt{opponent\_location\_x/y} & Opponent pixel position \\
\texttt{hit\_x/y}, \texttt{landing\_x/y} & Shuttle contact and landing coordinates \\
\texttt{backhand}, \texttt{hit\_height} & Additional shot context (partially missing) \\
\bottomrule
\end{tabular}
\end{table}

%----------------------------------------------------------------------
\section{Dataset Pre-processing}
%----------------------------------------------------------------------

From the frames we extract player skeletons, shuttlecock trajectories, and
player court positioning. The pipeline outputs $(2, 16, 34)$ skeleton tensors
per shot --- the direct input to the encoder.

\subsection{Skeleton Extraction}

\textbf{Pose Extraction.} Skeleton keypoints are extracted using YOLOv8-Pose
(yolov8s-pose), which performs joint person detection and 17-joint COCO
keypoint estimation in a single forward pass. For each frame, all detected
persons are scored by their mean keypoint confidence; the top-2 detections
are retained as the two players. Temporal smoothing is applied via an
exponential filter ($\alpha=0.7$) across the keypoint sequence for stability. Kalman
filtering is a planned upgrade for improved handling of occlusion frames.

\textbf{Quality audit --- umpire contamination.} A systematic audit of the extracted
FineBadminton skeletons revealed a significant contamination issue. YOLOv8-Pose
selects the top-2 persons by mean keypoint confidence per frame with no spatial
constraint. The chair umpire is consistently detected with high confidence
because they are stationary, upright, and well-lit --- occupying a seat at the
left edge of the court at approximately $x \approx 102$px on a 1280px-wide frame.
In frames where fewer than 2 players are confidently detected, the pipeline
falls back to the umpire as the second ``player'' and forward-fills those frames.

\textbf{Grounding DINO-guided extraction (adopted solution).} A GDINO-guided
approach uses Grounding DINO (grounding-dino-tiny) with the text prompt
\texttt{"badminton player ."} to produce court-region bounding boxes before YOLOv8
keypoint estimation. Only YOLO detections with IoU $\geq 0.25$ against a GDINO
bounding box are accepted as valid players. If fewer than 2 valid players pass
this filter, the pipeline falls back to plain YOLOv8 top-2 selection.
Additionally, a \textbf{spatial court-region mask} filters all detections (both
GDINO priors and YOLO candidates) to the central 76\% of the frame width
(x: 12\%--88\%) and enforces a minimum bounding box height of 10\% of frame
height. This eliminates chair umpires (seated at $x \approx 5$--10\%), line judges, and
ball kids from the candidate set before IoU matching. The fallback (plain top-2
YOLO when GDINO provides fewer than 2 priors) applies the same spatial filter,
preventing contamination even when GDINO fails. This approach substantially
reduces umpire contamination in the extracted skeletons.

The FineBadminton skeletons used in all experiments were extracted with the
GDINO-guided pipeline. All 40 rallies (10,620 frames) were successfully
extracted.

\subsection{Player Ordering and Hitter Assignment}

\textbf{Player ordering (Y-sort).} After selecting the top-2 detections, both
players are sorted by their mean Y keypoint centroid in image coordinates.
Since image Y increases downward:

\begin{itemize}
  \item Player 0 (joints 0--16) = smaller mean Y = top-court player
  \item Player 1 (joints 17--33) = larger mean Y = bottom-court player
\end{itemize}

This assignment is made purely from the extracted image geometry --- no
annotations are consulted. The resulting $(2, T, 34)$ skeleton arrays saved to
disk always follow this Y-sort convention. In the UI, the hitter is always
highlighted in a blue box and the opponent in a pink box --- this is done by
coloring only; the skeleton data itself is never reordered for display.

\textbf{Hitter ordering.} For the few-shot classifier to generalize across rallies
where either player may be the hitter, we always place the hitting player at
nodes 0--16 at dataset load time. This is done by conditionally swapping the two
17-joint halves via \texttt{\_reorder\_hitter\_first(segment, "top"|"bottom")}. If
\texttt{hitter == "bottom"}, nodes 0--16 and 17--33 are swapped after windowing. If
\texttt{hitter == "top"}, no swap is needed (the Y-sorted Player 0 is already the
hitter).

Both datasets derive hitter identity the same way. For FineBadminton, each
shot's annotation directly specifies the hitter's court side as \texttt{"top"} or
\texttt{"bottom"}. For ShuttleSet, the \texttt{player} column (\texttt{A} or \texttt{B}) identifies who hit
each shot, and the annotated \texttt{player\_location\_y} (pixel Y of the hitter)
determines which court side each player occupies. Since the broadcast camera
angle places the net well above the frame midpoint, a fixed pixel threshold
would misclassify most shots. Instead, for each rally we compute the median
\texttt{player\_location\_y} for Player A and Player B separately --- the player with the
smaller median Y is on the top court for that rally. This per-rally median
approach yields the expected 50/50 top--bottom split across all matches.

Result: for both datasets, every model input has the same semantics --- nodes
0--16 are the hitting player, nodes 17--33 are the opponent. The per-rally \texttt{.npy}
files on disk are always raw Y-sorted and are never modified; the hitter-first
swap is applied only in memory at dataset load time.

\subsection{Shot Segmentation (Temporal Windowing)}

Each shot sample is a $T=16$ frame window centered on the hit frame, spanning
$\pm 8$ frames ($\approx 0.8$~s at 20fps). This captures the preparation phase before
contact (footwork direction, racket windup) and the follow-through after
contact (net approach confirmation, opponent repositioning). Frames before the
hit are critical --- strategy is committed to during preparation, not at
contact. See Appendix~\ref{app:windowing} for full rationale.

For FineBadminton, windowing happens at dataset load time from the per-rally
\texttt{.npy} files using the annotated \texttt{hit\_frame}. For ShuttleSet, windowing
happens at extraction time; per-shot \texttt{.npy} files are already shape $(2,16,34)$.

\subsection{Shuttlecock Trajectory}

Shuttle trajectories are extracted using \textbf{TrackNetV4} (\texttt{tracknet-series-pytorch},
local clone). V4 adds a learnable \texttt{MotionPrompt} layer (inter-frame difference
attention) over the V2 U-Net baseline, which is particularly effective for a
fast-moving object like a shuttlecock moving 50--100 pixels per frame.

Outputs: per-rally \texttt{.npy} files of shape $(T, 3)$ --- columns $[x, y, \text{visible}]$,
frame-aligned with the skeleton arrays. These are stored in
\texttt{datasets\_preprocessing/finebadminton\_shuttles/} and visualized in the demo UI
as a yellow dot + trail overlay.

Shuttle trajectory is optionally incorporated as \textbf{virtual node 34} in the
dual-player graph (35 nodes total). When \texttt{use\_shuttle=True}, the shuttle's
$(x, y)$ position is appended before feature engineering so that the homography
transform applies to it, making all distance/velocity features camera-invariant.
The shuttle node is connected to both players' wrist joints (nodes 9, 10 for P1;
26, 27 for P2) in the ST-GCN graph. This is evaluated as \textbf{Step 6} in the
ablation study (skeleton-only 34-node vs. skeleton+shuttle 35-node graph).

\subsection{Player Court Position}

Accurate court-relative coordinates are needed for the L2 node features
(dist\_to\_net, dist\_to\_center, dist\_to\_opponent). Two approaches are available:

\textbf{Option 1 --- Player-span normalization (no external calibration required).}
Normalize Y coordinates using the two players' centroid positions:

\begin{lstlisting}[language=Python]
p0_cy = skeleton[1, :, :17].mean(axis=-1, keepdims=True)   # (T, 1)
p1_cy = skeleton[1, :, 17:].mean(axis=-1, keepdims=True)
span  = (p1_cy - p0_cy).clip(min=1)
y_norm = (skeleton[1] - (p0_cy + p1_cy) / 2) / span        # y=0 ~ net
\end{lstlisting}

This maps P0 centroid $\to$ $y = -0.5$ (top-court baseline), P1 centroid $\to$
$y = +0.5$ (bottom-court baseline), net $\to$ $y \approx 0$. It is fully self-contained per
shot and requires no external model. Less accurate than homography (assumes
player centroids span half-courts evenly) but a large improvement over raw
pixels.

\textbf{Option 2 --- Full homography (most accurate; required for Phase C inference).}
A $3\times3$ perspective transform $H$ maps pixel coordinates $(u, v)$ to court-relative
meters $(x, y)$ with origin at court center. For FineBadminton (fixed broadcast
camera), $H$ is computed once per resolution group. For ShuttleSet, $H$ is computed
per match. For Phase C (new unseen video), $H$ is detected automatically via
Canny edge detection + probabilistic Hough transform + RANSAC fitting against
a standard badminton court template ($13.4\text{m} \times 6.1\text{m}$ for singles). Manual fallback
allows clicking four court corners in a reference frame ($\approx$10 seconds of effort).

\textbf{Perspective elevation error and mitigation.} A homography is defined on the
court floor plane ($z = 0$), so it maps floor-level points exactly. However,
skeleton joints are elevated above the floor --- the torso by $\approx$1~m and the head
by $\approx$2~m. Under a typical broadcast camera (elevated $\approx$10~m, tilted $\approx$15--20\textdegree{} down),
elevated joints on the far-side player (top court) appear shifted \emph{toward} the
camera in image space, causing the homography to project their body centroid past
the net into the opponent's half. Three mitigations
were evaluated in notebook 07: (A) ankle-only positioning, using only joints 15
and 16 (left/right ankle) which lie on the floor plane --- this is the adopted
approach; (B) hip-midpoint positioning (joints 11--12); and (C) depth-corrected positioning using Depth
Anything V2 Small. Approach A is adopted as the default because ankle detections are reliable and the
floor-plane assumption is exactly satisfied.

%----------------------------------------------------------------------
\section{Model Training}
%----------------------------------------------------------------------

\subsection{Few-Shot Training Setup}

Given the extremely small labeled set (40 rallies), the evaluation protocol
uses \textbf{rally-level 5-fold cross-validation} over all 40 rallies ($\sim$8 test
rallies per fold, $\sim$24 train, $\sim$8 val for checkpoint selection).

\textbf{Why rally-level (not shot-level) splitting:} Shots within the same rally
share the same skeleton file and the same two players across consecutive
frames. Shot-level k-fold places shots from the same rally in both train and
test (empirically 25--28 of 40 rallies appear in both splits every fold),
meaning the model has already seen those players' movement patterns at test
time. Rally-level splitting ensures every test shot comes from a rally whose
players were never seen during training, giving an honest generalisation
estimate. All 40 rallies contribute to evaluation via rotation across folds.

\textbf{Split design (per fold):}
\begin{itemize}
  \item $\sim$24 rallies --- episodic ProtoNet training
  \item $\sim$8 rallies --- validation (checkpoint selection only)
  \item $\sim$8 rallies --- test (reported metrics)
\end{itemize}

All results report mean $\pm$ standard deviation across folds. Class distribution
is imbalanced (intercept and passive are more common than move\_to\_net). We
address this through balanced episodic sampling during meta-training: each
episode samples equal numbers of support and query examples per class
regardless of overall class frequency.

\textbf{Phase B baseline (no SSL pre-training, completed).} Setup: L2 features
(9-dim), ST-GCN encoder (3.1M params) randomly initialized, episodic
meta-training (50 epochs $\times$ 100 episodes, 5-way 10-shot), fine-tune encoder
during Phase B. Data: 296 labeled shots across 40 GDINO-guided rallies. Run
on Colab T4 GPU.

\textbf{Overall result: Macro-F1 = 37.0\% $\pm$ 3.3\%}

\begin{table}[H]
\centering
\small
\begin{tabular}{lrrrr}
\toprule
\textbf{Fold} & \textbf{Train loss (ep.50)} & \textbf{Train acc} & \textbf{Best Val-F1} & \textbf{Test Macro-F1} \\
\midrule
1 & 0.049 & 0.983 & 0.519 & 0.409 \\
2 & 0.041 & 0.986 & 0.337 & 0.375 \\
3 & 0.034 & 0.990 & 0.326 & 0.333 \\
4 & 0.040 & 0.988 & 0.486 & 0.331 \\
5 & 0.022 & 0.991 & 0.396 & 0.399 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Per-class F1 (mean $\pm$ std across 5 folds):}

\begin{table}[H]
\centering
\small
\begin{tabular}{lrrrp{5cm}}
\toprule
\textbf{Strategy} & \textbf{Samples} & \textbf{Mean F1} & \textbf{Std} & \textbf{Observation} \\
\midrule
create\_depth & 61 & 0.581 & 0.087 & Best-performing class despite moderate count \\
intercept & 108 & 0.522 & 0.074 & Most common class, consistent across folds \\
defensive & 59 & 0.417 & 0.085 & Moderate performance \\
passive & 50 & 0.290 & 0.130 & High variance; confused with intercept/defensive \\
\textbf{move\_to\_net} & \textbf{18} & \textbf{0.036} & \textbf{0.073} & \textbf{Near-zero in 4/5 folds --- insufficient samples} \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Key observations:}

\begin{enumerate}
  \item Result is within the expected 35--45\% range for random-init condition,
    confirming the experimental design is sound.
  \item \textbf{Severe episodic overfitting.} Training accuracy reaches 98--99\% while
    validation F1 peaks at epoch 10 and degrades thereafter. SSL pre-training
    is expected to be the primary fix.
  \item \textbf{\texttt{move\_to\_net} is effectively unlearnable at this scale} (18 samples,
    6.1\% of dataset). ProtoNet prototype is noise-dominated.
  \item \textbf{\texttt{create\_depth} outperforms \texttt{intercept}} despite fewer samples (61 vs 108),
    suggesting create\_depth has more distinctive skeleton signatures (rear-court
    positioning, extended arm overhead).
  \item \textbf{ProtoNet > Linear probe > k-NN} (relative, from single-fold comparison).
    The centroid assumption holds --- the embedding space (even random-init) creates
    roughly spherical per-class clusters.
\end{enumerate}

\subsection{SSL Pre-Training (Phase A) --- Supervised Contrastive Learning}

We apply \textbf{SupCon (Supervised Contrastive Learning; Khosla et al., 2020)}
using ShuttleSet's shot-type labels as supervision. Unlike SimCLR which pairs
augmented views of the same sample, SupCon treats all shots of the same type
(across different players and matches) as positives. This forces the encoder
to cluster by shot mechanics (smash trajectory, drop placement, lob height)
rather than by player identity or match context.

\textbf{Training objective:}

For a batch of skeleton sequences $\{x_i\}$, let $y_i$ be the shot-type label:

\begin{equation}
\mathcal{L}_{\text{SupCon}} = \sum_{i} \left[ \frac{-1}{|P(i)|} \cdot \sum_{p \in P(i)} \log \frac{\exp(z_i \cdot z_p / \tau)}{\sum_{a \neq i} \exp(z_i \cdot z_a / \tau)} \right]
\end{equation}

where $P(i) = \{j : y_j = y_i, j \neq i\}$ is the set of same-type positives in
the batch, $z_i$ is the L2-normalized projection head output, and $\tau=0.07$ is the
temperature.

\textbf{Skeleton augmentations} (applied independently to both views):
\begin{itemize}
  \item Joint coordinate jittering (Gaussian noise $\sigma=0.02$)
  \item Temporal crop and resample ($\pm$20\% window)
  \item Spatial rotation ($\pm$15\textdegree{} court-relative)
  \item Joint masking (10--20\% of joints zeroed)
\end{itemize}

\textbf{Training data:} 15 SS train-split matches ($\sim$12,700 shots). The 5 validation
matches are held out for shot-type linear probe evaluation. Since SupCon uses
shot-type labels rather than strategy labels, there is no strategy label leakage.

\textbf{Benefit over SimCLR:} The auxiliary shot-type classification head previously
required separate loss weighting and competed with the contrastive objective.
SupCon integrates shot-type supervision directly into the contrastive loss,
producing semantically structured embeddings in a single objective.

%----------------------------------------------------------------------
\section{Architecture \& Pipeline}
%----------------------------------------------------------------------

\subsection{End-to-End Pipeline}

The system comprises three phases executed sequentially:

\begin{itemize}
  \item \textbf{Phase A (SSL pre-training):} Unlabeled ShuttleSet data $\to$ encoder learns
    general badminton motion features via contrastive learning.
  \item \textbf{Phase B (few-shot adaptation):} Small FineBadminton labeled set $\to$ ProtoNet
    maps learned features to 5 tactical strategy classes.
  \item \textbf{Phase C (inference):} New unseen video $\to$ automatic court detection + shot
    boundary detection + full feature-to-prediction cascade.
\end{itemize}

\begin{table}[H]
\centering
\caption{End-to-end pipeline stages}
\label{tab:pipeline}
\small
\begin{tabularx}{\textwidth}{llXX}
\toprule
\textbf{Stage} & \textbf{Component} & \textbf{Input} & \textbf{Output} \\
\midrule
A1 & YOLOv8-Pose (GDINO-guided) & Video frames & 2D skeletons (17 joints $\times$ 2 players), Y-sorted, exponentially smoothed \\
A2 & Graph Builder + Feature Eng. & Skeleton sequences & Spatio-temporal graph $G=(V,E,X)$ with enriched node features (L0--L3) \\
A3 & Shot Segmentation & Skeleton graphs + timestamps & $T=16$ frame windows per shot, hitter-first ordered \\
A4 & ST-GCN Encoder & Skeleton graph & 256-dim motion embedding \\
A5 & SupCon Head & Augmented skeleton pairs + shot-type labels & Supervised contrastive loss (same-type = positive) \\
A6 & Shot-Type Classifier & Frozen encoder embeddings (SS train) & Logistic head saved for inference \\
B1 & Prototype Computation & FB labeled support embeddings & 5 class prototypes (mean vectors) \\
B2 & ProtoNet Classifier & Query embedding + prototypes & Strategy label + confidence score \\
C1 & Frame Extraction (ffmpeg) & New video (.mp4) & Frames at 30fps \\
C2 & Court Detector (Hough + RANSAC) & Reference frame & Homography $H$ (pixel $\to$ court coords) \\
C3 & TrackNetV3 (pre-trained, frozen) & Consecutive frames & Shuttle $(x,y)$ per frame + hit event timestamps \\
C4 & YOLOv8-Pose & All frames & Skeleton keypoints (17 joints $\times$ 2 players) \\
C5 & Shot Segmentation & Hit timestamps + skeletons & $T=16$ frame windows per shot \\
C6 & Feature Engineering (L0--L3) & Skeleton windows + $H$ & Enriched node features in court-relative coords \\
C7 & Encoder (Phase A weights) & Enriched skeleton graphs & 256-dim embedding per shot \\
C8 & ProtoNet (Phase B prototypes) & Embeddings + prototypes & Strategy label + confidence score + margin \\
C9 & Shot-Type Head (Phase A weights) & Same embedding & Shot-type label + confidence (17 classes) \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{Graph Construction}

The dual-player spatio-temporal graph uses a unified graph with \textbf{34 nodes}
(17 joints per player). Intra-player edges follow the standard COCO skeleton
topology (anatomical connections). Inter-player edges connect corresponding
joints between players (e.g., right wrist to right wrist) to capture relative
positioning. The adjacency matrix $A$ combines three sub-matrices: $A_{\text{intra1}}$
(player 1 skeleton), $A_{\text{intra2}}$ (player 2 skeleton), and $A_{\text{inter}}$ (cross-player
relations). Temporal edges connect each joint to itself in adjacent frames
(default window $w=1$, ablation with $w=3$).

\subsection{Node Feature Engineering}

Raw skeleton coordinates alone are an impoverished input. The strategy
taxonomy requires the model to perceive velocity, court context, body
configuration, and inter-player spatial relationships. We compute enriched
node features in cumulative layers:

\begin{table}[H]
\centering
\caption{Node feature layers (cumulative)}
\label{tab:features}
\small
\begin{tabularx}{\textwidth}{llrX}
\toprule
\textbf{Layer} & \textbf{Features per node} & \textbf{Dim} & \textbf{Signal encoded} \\
\midrule
L0: Raw coordinates & $[x, y]$ court-relative via homography & 2 & Position only \\
L1: + Kinematics & $[x, y, v_x, v_y, a_x, a_y]$ finite differences & 6 & Velocity encodes ``lunging forward'' (intercept) vs. ``stationary'' (passive) \\
L2: + Court context & $[\ldots, d_{\text{net}}, d_{\text{center}}, d_{\text{opp}}]$ & 9 & Court position encodes ``forward court'' (intercept) vs. ``rear court'' (defensive) \\
L3: + Joint angles & $[\ldots, \theta_{\text{elbow}}, \theta_{\text{knee}}, \theta_{\text{shoulder}}]$ & 12 & Body pose encodes ``arm extended'' (defensive) vs. ``arm forward flat'' (intercept) \\
L4: + Racket (stretch) & $[\ldots, r_x, r_y, r_\theta]$ as 18th node & 14--15 & Shot direction --- requires RacketVision (stretch goal) \\
\bottomrule
\end{tabularx}
\end{table}

Layers L0--L3 are computable from existing skeleton coordinates with simple
numpy operations (finite differences, Euclidean distances, arctan2). They
require no additional data or models. Layer L4 requires running RacketVision
on frames and is treated as a stretch goal.

\subsection{ST-GCN Encoder}

The ST-GCN encoder applies graph convolutions alternating between spatial
graph operations (over the 34-node skeleton topology) and temporal convolutions
(over the $T=16$ frame sequence). 9 ST-GCN blocks produce a final 256-dim
embedding per shot. The architecture is configurable via \texttt{DataConfig} and
\texttt{STGCNConfig} in \texttt{src/config.py}. Input channel dimension changes from 2 to 6
to 9 to 12 across feature layers L0--L3 with zero architectural modification.

An alternative Transformer encoder (BST-style) is implemented for future
encoder comparison but is not part of the current ablation scope (see \S\ref{sec:future}).

\subsection{Prototypical Network Classifier}

Phase B is near-parameter-free. The ProtoNet operates in two steps:

\begin{enumerate}
  \item \textbf{Prototype computation:} For each of the 5 strategy classes, compute the
    mean embedding (centroid) of all support examples in that class. With 32
    support rallies per fold, each prototype averages approximately 6--8 shot
    embeddings. No gradient descent, no loss function.
  \item \textbf{Distance-based classification:} Compute Euclidean distance from a query
    shot's embedding to each of the 5 prototypes. Assign to the nearest.
    Confidence is derived from softmax over negative distances; margin score
    (nearest vs. second-nearest distance) flags low-confidence predictions.
\end{enumerate}

%----------------------------------------------------------------------
\section{Results \& Key Findings}
\label{sec:results}
%----------------------------------------------------------------------

\subsection{Main Results Table}

\begin{table}[H]
\centering
\caption{Main results --- encoder $\times$ pre-training (values filled as experiments complete)}
\label{tab:main-results}
\small
\begin{tabularx}{\textwidth}{lllrX}
\toprule
\textbf{Encoder} & \textbf{Pre-training} & \textbf{Classifier} & \textbf{Macro-F1} & \textbf{Notes} \\
\midrule
Random baseline & --- & uniform & $\sim$20.0\% & Theoretical floor (uniform 5-class) \\
Majority class & --- & always ``intercept'' & $\sim$15.6\% & Always predict majority class \\
\textbf{ST-GCN + ProtoNet} & \textbf{None (random init)} & \textbf{5-way 10-shot} & \textbf{36.9\% $\pm$ 3.3\%} & Done --- L2, GDINO, episodic fine-tune \\
ST-GCN + ProtoNet & SupCon (shot type, L2) & 5-way 10-shot (frozen enc) & 55.9\% $\pm$ 8.9\% & Done (preliminary --- frozen enc, not fine-tuned) \\
\textbf{ST-GCN + ProtoNet} & \textbf{SupCon (shot type, L2)} & \textbf{5-way 10-shot (fine-tuned)} & \textbf{[TBD]} & \textbf{Primary target --- RQ2} \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{Per-Strategy F1 by Feature Layer (Step 1a)}

\begin{table}[H]
\centering
\caption{Per-strategy F1 across input feature layers (Step 1a ablation --- pending Colab run)}
\label{tab:perstrategy}
\small
\begin{tabular}{lrrrr}
\toprule
\textbf{Strategy} & \textbf{L0 (x,y)} & \textbf{L1 (+vel,accel)} & \textbf{L2 (+court ctx) --- random init} & \textbf{L3 (+angles)} \\
\midrule
create\_depth & [TBD] & [TBD] & \textbf{0.581} & [TBD] \\
intercept & [TBD] & [TBD] & \textbf{0.522} & [TBD] \\
move\_to\_net & [TBD] & [TBD] & \textbf{0.036} & [TBD] \\
passive & [TBD] & [TBD] & \textbf{0.290} & [TBD] \\
defensive & [TBD] & [TBD] & \textbf{0.417} & [TBD] \\
\textbf{Macro-F1} & [TBD] & [TBD] & \textbf{0.369 $\pm$ 0.033} & [TBD] \\
\bottomrule
\end{tabular}
\end{table}

\emph{Note: L2 is the only layer with an SSL checkpoint; L0/L1/L3 comparisons use random init. This means the L2 advantage may partially reflect SSL pre-training rather than feature engineering alone --- a known limitation of the sequential ablation design.}

\subsection{Expert-Verified Strategy Evaluation (SS Validation Set)}
\label{sec:expert-eval}

As a qualitative cross-dataset evaluation, the trained system is applied to
the 5 SS validation matches. For each shot the model outputs both a
\textbf{strategy prediction} (5 classes, confidence score) and a \textbf{shot-type
prediction} (17 classes). A domain expert reviews shots where strategy
confidence exceeds a threshold (e.g. $\geq 0.75$), confirming or rejecting each
prediction. This produces:

\begin{itemize}
  \item \textbf{Precision at threshold:} fraction of high-confidence strategy predictions
    confirmed by expert
  \item \textbf{Shot-type accuracy:} automatic metric (ground truth from SS CSVs), used
    as a sanity check that the encoder is functioning correctly
  \item \textbf{Qualitative examples:} rally visualisations showing skeleton overlaid with
    predicted strategy and shot type per frame, reviewed for coherence
\end{itemize}

This evaluation is intentionally qualitative --- ShuttleSet has no strategy
labels --- but provides meaningful evidence that the representation generalises
across datasets. High shot-type accuracy (proxy) combined with expert-confirmed
strategy predictions constitutes a sufficient cross-dataset validity check
for a few-shot system.

\subsection{Graph Structure Contribution (Step 1b)}

\begin{table}[H]
\centering
\caption{Macro-F1 by graph topology --- does the opponent skeleton matter?}
\label{tab:graph}
\small
\begin{tabular}{lrl}
\toprule
\textbf{Variant} & \textbf{Nodes} & \textbf{Macro-F1} \\
\midrule
full\_dual & 34 & [TBD] \\
no\_inter\_edges & 34 & [TBD] \\
single\_player & 17 & [TBD] \\
\bottomrule
\end{tabular}
\end{table}

\emph{Note: RQ1 (spatial vs. temporal contribution) is addressed indirectly by comparing L0 (position only) vs. L1 (+ velocity/acceleration) in Step 1a, rather than by disabling spatial/temporal conv layers.}

\subsection{Ablation Plan Summary}

Six ablation steps are run sequentially, each varying one axis while holding
all others fixed at the best value found so far. Steps 1a and 1b are separated
because feature engineering and graph topology answer distinct questions.

\begin{lstlisting}[basicstyle=\ttfamily\footnotesize]
STEP 1a -- FEATURE ENGINEERING (fix encoder=ST-GCN, graph=full dual-player)
|-- L0: Raw [x, y] joint coordinates only                (2-dim)
|-- L1: + velocity, acceleration                         (6-dim)
|-- L2: + dist_to_net, dist_to_center, dist_to_opponent  (9-dim) <- baseline done (37.0%)
+-- L3: + elbow, shoulder, knee angles                   (12-dim)

STEP 1b -- GRAPH STRUCTURE (fix feature_layer = best from Step 1a)
|-- full_dual:      34 nodes, inter-player edges = Yes   <- default
|-- no_inter_edges: 34 nodes, inter-player edges = No
+-- single_player:  17 nodes (hitter only)

STEP 2 -- PRE-TRAINING REGIME (RQ2) (fix encoder=ST-GCN, input = best from Step 1)
|-- random_init:    no pre-training                       <- baseline: 36.9%
|-- simclr:         SimCLR (self-supervised, no labels)
+-- supcon:         SupCon (shot-type labels as positives)

STEP 3 -- FEW-SHOT CLASSIFIER (fix all above = best)
|-- ProtoNet        <- nearest centroid (preliminary: 55.9% +/- 8.9%)
|-- k-NN (k=3)     <- (preliminary: 53.5% +/- 11.7%)
|-- k-NN (k=5)     <- (preliminary: 54.5% +/- 9.4%)
+-- Linear probe    <- logistic regression (preliminary: 51.5% +/- 9.5%)

STEP 4 -- K-SHOT SENSITIVITY (final best configuration)
+-- K = 1, 3, 5, 8, 10
\end{lstlisting}

\subsection{Planned Visualizations}

\begin{itemize}
  \item \textbf{t-SNE / UMAP embedding plots:} colored by strategy class, comparing
    random-init vs. SSL-pretrained embeddings.
  \item \textbf{Confusion matrix:} $5\times5$ matrix showing per-class error patterns. Expect
    defensive/passive confusion (both involve reactive body postures).
  \item \textbf{K-shot learning curve:} F1 as a function of K (1--15), showing diminishing
    returns and minimum viable supervision.
  \item \textbf{Graph attention maps:} which joints and temporal frames receive highest
    attention per strategy class.
\end{itemize}

%----------------------------------------------------------------------
\section{Implementation}
%----------------------------------------------------------------------

\subsection{Codebase Structure}

\begin{table}[H]
\centering
\caption{Module responsibilities}
\label{tab:modules}
\small
\begin{tabularx}{\textwidth}{lXl}
\toprule
\textbf{File} & \textbf{Responsibility} & \textbf{Stage} \\
\midrule
\texttt{src/config.py} & Hyperparameters, file paths, experiment settings & Global \\
\texttt{src/data/pose\_extractor.py} & YOLOv8s-Pose skeleton extraction (GDINO-guided) & A1/C4 \\
\texttt{src/data/graph\_builder.py} & Dual-player spatio-temporal graph (34 nodes) & A2 \\
\texttt{src/data/dataset.py} & Data loading, shot windowing, hitter-first ordering & Data \\
\texttt{src/models/stgcn\_model.py} & ST-GCN backbone (9 blocks); 3.08M params & A4/C7 \\
\texttt{src/models/transformer\_encoder.py} & BST-style Transformer encoder (future) & Future \\
\texttt{src/models/simclr\_loss.py} & NT-Xent contrastive loss, projection head & A5 \\
\texttt{src/models/proto\_net.py} & ProtoNet + k-NN, confidence/margin scoring & B1--B2/C8 \\
\texttt{src/inference.py} & Phase C end-to-end inference & C1--C8 \\
\texttt{badminton\_server.py} & HTTP demo server (port 7860) & Demo \\
\texttt{badminton\_pipeline\_demo.html} & Standalone React+Babel demo UI & Demo \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{Technical Stack}

\begin{itemize}
  \item \textbf{Framework:} PyTorch 2.x with PyTorch Geometric for graph operations.
  \item \textbf{Pose Estimation:} YOLOv8s-Pose --- combined person detection + 17-joint
    COCO keypoint estimation. Top-2 detections by mean keypoint confidence. Temporal smoothing via exponential filter ($\alpha=0.7$).
  \item \textbf{Player Filtering:} Grounding DINO (grounding-dino-tiny) with text prompt
    \texttt{"badminton player ."} for umpire-rejection.
  \item \textbf{Shuttle Tracking (preprocessing):} TrackNetV4 (\texttt{tracknet-series-pytorch}).
  \item \textbf{Shuttle Tracking (inference):} TrackNetV3 (pre-trained, frozen).
  \item \textbf{Court Detection:} OpenCV Canny + probabilistic Hough + RANSAC
    homography estimation against a $13.4\text{m} \times 6.1\text{m}$ badminton court template.
  \item \textbf{Video Processing:} yt-dlp for ShuttleSet download; ffmpeg for frame extraction at 30fps.
  \item \textbf{Compute:} Google Colab Pro (T4/A100 GPU). Estimated $\sim$8 hours for SSL
    pre-training, $\sim$1 hour for few-shot training, $\sim$30--60 seconds per rally for Phase C inference.
  \item \textbf{Reproducibility:} All random seeds fixed. \texttt{config.py} stores all
    hyperparameters. Experiment tracking via Weights \& Biases.
\end{itemize}

\subsection{Data Directory Structure}

\begin{lstlisting}[basicstyle=\ttfamily\footnotesize]
Baddiev2/
+-- Datasets/                       # Raw datasets (provided/downloaded)
|   +-- FineBadminton-dataset/dataset/
|   |   +-- image/                  # 10,620 .jpg frames (all 40 rallies)
|   |   +-- transformed_combined_rounds_output_en_evals_translated.json
|   +-- finebadminton_skeletons/    # (legacy path -- not used)
|
+-- datasets/                       # Cloned repos and tools
|   +-- ShuttleSet/set/match.csv    # ShuttleSet CSV annotations
|   +-- tracknet-series-pytorch/    # TrackNetV4 implementation
|
+-- datasets_preprocessing/         # All extracted/processed data
|   +-- finebadminton_skeletons/    # 40 per-rally .npy (2, T, 34)
|   +-- finebadminton_shuttles/     # 40 per-rally .npy (T, 3)
|   +-- ShuttleSet/
|       +-- frames/                 # Extracted video frames
|       +-- skeletons/              # Per-shot .npy (2, 16, 34)
|
+-- models/                         # Saved model checkpoints
+-- src/                            # All reusable Python source code
+-- notebooks/                      # All Jupyter notebooks
+-- badminton_server.py             # Demo HTTP server (port 7860)
+-- badminton_pipeline_demo.html    # Standalone React+Babel demo UI
\end{lstlisting}

\textbf{Key conventions:}
\begin{itemize}
  \item \texttt{Datasets/} (capital D): raw provided data, never modified
  \item \texttt{datasets/} (lowercase): cloned third-party repos and tools
  \item \texttt{datasets\_preprocessing/}: all outputs of extraction notebooks
  \item Per-rally skeleton \texttt{.npy} shape: $(2, T, 34)$ --- axis 0 = coord channel (X/Y),
    axis 1 = frame, axis 2 = joint (0--16 = player 0, 17--33 = player 1)
  \item Per-rally shuttle \texttt{.npy} shape: $(T, 3)$ --- columns = $[x, y, \text{visible}]$;
    frame-aligned with skeleton array
\end{itemize}

%----------------------------------------------------------------------
\section{Limitations \& Future Work}
\label{sec:future}
%----------------------------------------------------------------------

\subsection{Current Limitations}

\begin{itemize}
  \item \textbf{Small test set variance:} With 4 test rallies per fold ($\sim$50--65 shots),
    a single misclassified rally can shift macro-F1 by 5--10 percentage points.
    Mitigated by 5-fold CV and confidence intervals, but results should be
    interpreted accordingly.
  \item \textbf{Class imbalance:} \texttt{move\_to\_net} has only 18 training samples (6.1\%),
    making its prototype noise-dominated and near-unlearnable at this scale.
  \item \textbf{2D skeleton limitations:} We use 2D pose estimation, losing depth
    information that could help distinguish strategies (e.g., shuttle height for
    create\_depth). 3D pose lifting (MotionBERT) is a potential extension.
  \item \textbf{No shuttle trajectory in encoder:} Several strategies (create\_depth,
    intercept) are partially defined by shuttle placement. TrackNetV4 trajectories
    are extracted and visualized in the demo but not yet incorporated as encoder
    input during Phases A--B.
  \item \textbf{Pose estimation errors:} Occlusion, fast motion blur, and overlapping
    players cause pose estimation failures. The GDINO filter substantially reduces
    umpire contamination but does not eliminate all errors.
  \item \textbf{Domain gap:} Pre-training and evaluation both use broadcast footage.
    Generalization to amateur phone recordings is an unvalidated claim.
  \item \textbf{Frame rate mismatch:} FineBadminton at $\sim$20fps, ShuttleSet at 30fps.
    Temporal resampling or rate-agnostic segmentation is needed for consistent
    window semantics across datasets.
\end{itemize}

\subsection{Future Work}

\begin{itemize}
  \item \textbf{Encoder architecture comparison (ST-GCN vs Transformer):} The Transformer
    encoder is implemented but not evaluated. A direct comparison against ST-GCN
    on the same few-shot task would answer whether graph-structural priors help
    or whether attention-based models can match performance without them.
  \item \textbf{Shuttle trajectory as encoder input (highest priority):} Integrate the
    extracted TrackNetV4 trajectories as a 35th graph node or global graph-level
    feature during Phases A--B training.
  \item \textbf{3D pose lifting:} Replace 2D pose estimation with monocular 3D lifting
    (MotionBERT, MotionAGFormer) to recover depth.
  \item \textbf{Rally-level temporal modeling:} Extend from shot-level to rally-level
    sequence modeling (Transformer over shot embeddings) to capture multi-shot
    strategic arcs.
  \item \textbf{Active learning:} Use the confidence estimation module to identify the
    most informative unlabeled rallies for expert annotation.
  \item \textbf{Learning-based court detection:} Replace Hough + RANSAC with a trained
    court keypoint detector for robustness on amateur footage.
  \item \textbf{Cross-sport transfer:} Evaluate the pre-trained encoder on tennis, squash,
    and table tennis tactical analysis.
\end{itemize}

%----------------------------------------------------------------------
\section{References}
%----------------------------------------------------------------------

\begin{thebibliography}{11}

\bibitem{wang2022}
Wang, W.~Y., et al. (2022).
\newblock ShuttleNet: Position-aware Fusion of Rally Progress and Player Styles for Stroke Forecasting in Badminton.
\newblock \emph{Proceedings of the AAAI Conference on Artificial Intelligence.}

\bibitem{finebadminton}
FineBadminton Dataset.
\newblock Fine-grained badminton annotations with strategy labels, shot subtypes, and quality scores.
\newblock [Dataset paper reference TBD upon access].

\bibitem{yan2018}
Yan, S., Xiong, Y., \& Lin, D. (2018).
\newblock Spatial Temporal Graph Convolutional Networks for Skeleton-Based Action Recognition.
\newblock \emph{Proceedings of the AAAI Conference on Artificial Intelligence.}

\bibitem{snell2017}
Snell, J., Swersky, K., \& Zemel, R. (2017).
\newblock Prototypical Networks for Few-shot Learning.
\newblock \emph{Advances in Neural Information Processing Systems.}

\bibitem{li2021}
Li, L., et al. (2021).
\newblock CrosSCLR: Cross-View Contrastive Learning for 3D Skeleton-Based Action Recognition.
\newblock \emph{Proceedings of CVPR.}

\bibitem{guo2022}
Guo, T., et al. (2022).
\newblock AimCLR: Contrastive Learning of Skeleton-Based Action Recognition with Extreme Augmentations.
\newblock \emph{Proceedings of CVPR.}

\bibitem{chen2020}
Chen, T., et al. (2020).
\newblock A Simple Framework for Contrastive Learning of Visual Representations (SimCLR).
\newblock \emph{Proceedings of ICML.}

\bibitem{chang2025}
Chang, W. (2025).
\newblock BST: Badminton Stroke-type Transformer for Skeleton-Based Stroke Classification.
\newblock \emph{CVPR 2025 Workshop.}

\bibitem{dong2025}
Dong, Y., et al. (2025).
\newblock RacketVision: Racket Detection and Tracking in Badminton Video.
\newblock [Venue TBD].

\bibitem{sun2023}
Sun, Y., et al. (2023).
\newblock TrackNetV3: Real-Time Shuttlecock Tracking in Badminton.
\newblock \emph{Proceedings of ACM Multimedia.}

\bibitem{khosla2020}
Khosla, P., et al. (2020).
\newblock Supervised Contrastive Learning.
\newblock \emph{Advances in Neural Information Processing Systems (NeurIPS).}

\end{thebibliography}

%----------------------------------------------------------------------
\appendix
%----------------------------------------------------------------------

\section{Exploratory Data Analysis}
\label{app:eda}

This appendix reports factual statistics and annotation structure for both
datasets, as produced by the EDA notebooks.

\subsection{FineBadminton Dataset}

\textbf{Source and acquisition.} Frames are pre-extracted JPEGs organized by rally
ID (\texttt{\{rally\_id\}\_\{abs\_frame\}.jpg}). Annotations are in two JSON files; the
pipeline uses the English-translated version.

\textbf{Scale:}

\begin{table}[H]
\centering
\small
\begin{tabular}{lr}
\toprule
\textbf{Statistic} & \textbf{Value} \\
\midrule
Total rallies & 40 \\
Total hitting events & 414 \\
Shots with strategy labels & 355 (85.7\%) \\
Shots used in training & 296 \\
Total frames & 10,620 JPEG images \\
Rally frame length & min 73 $\cdot$ max 651 $\cdot$ mean 264 \\
Shots per rally & min 3 $\cdot$ max 27 $\cdot$ mean 10.3 \\
FPS range & $\sim$24.6--25.0 fps \\
Resolution mix & 1280$\times$720, 1912$\times$1080, 1920$\times$1080 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Shot type distribution (hit\_type, N=414):}

\begin{table}[H]
\centering
\small
\begin{tabular}{lrr}
\toprule
\textbf{Shot type} & \textbf{Count} & \textbf{\%} \\
\midrule
push shot & 84 & 20.3\% \\
kill & 70 & 16.9\% \\
net shot & 44 & 10.6\% \\
block & 43 & 10.4\% \\
serve & 40 & 9.7\% \\
drive & 34 & 8.2\% \\
clear & 31 & 7.5\% \\
drop shot & 23 & 5.6\% \\
cross-court net shot & 20 & 4.8\% \\
net lift & 16 & 3.9\% \\
net kill & 8 & 1.9\% \\
(unlabelled) & 1 & 0.2\% \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Quality score distribution (scale 1--7):}

\begin{table}[H]
\centering
\small
\begin{tabular}{l*{7}{r}}
\toprule
\textbf{Score} & 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
\midrule
Count & 11 & 27 & 70 & 136 & 108 & 32 & 30 \\
\% & 2.7 & 6.5 & 16.9 & 32.9 & 26.1 & 7.7 & 7.2 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Ball area distribution (court zone at contact, N=413):}

\begin{table}[H]
\centering
\small
\begin{tabular}{lr}
\toprule
\textbf{Zone} & \textbf{Count (\%)} \\
\midrule
mid front court & 85 (20.6\%) \\
left front court & 52 (12.6\%) \\
mid court & 47 (11.4\%) \\
right front court & 46 (11.1\%) \\
right mid court & 41 (9.9\%) \\
right back court & 38 (9.2\%) \\
left mid court & 37 (9.0\%) \\
left back court & 35 (8.5\%) \\
mid back court & 32 (7.7\%) \\
\bottomrule
\end{tabular}
\end{table}

Front-court shots dominate (44.3\%), consistent with the high frequency of net
shots, push shots, and blocks in elite men's singles.

\textbf{Shot characteristics and player actions (multi-label):}

\begin{table}[H]
\centering
\small
\begin{tabular}{lr|lr}
\toprule
\textbf{Characteristic} & \textbf{Count} & \textbf{Action} & \textbf{Count} \\
\midrule
cross-court & 241 & forehand & 254 \\
straight & 169 & backhand & 158 \\
over head & 96 & turnaround & 8 \\
body hit & 16 & & \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Hitter balance:} top-court hitter 206 shots (49.8\%), bottom-court hitter
207 shots (50.0\%), 1 missing. Near-perfect balance eliminates systematic bias.

\subsection{ShuttleSet Dataset}

\textbf{Scale:}

\begin{table}[H]
\centering
\small
\begin{tabular}{lr}
\toprule
\textbf{Statistic} & \textbf{Value} \\
\midrule
Total matches in match.csv & 44 \\
Excluded (wrong broadcast angle) & 4 \\
Usable broadcast-angle matches & 38 (of 44) \\
Matches with skeleton extracted & 20 \\
Total stroke records (20 matches) & $\sim$17,000 (est.) \\
Total rallies (20 matches) & $\sim$590 (est.) \\
Unique shot types (unified vocab) & 17 \\
Avg strokes per match & $\sim$847 \\
Class imbalance (most/least common) & $\sim$98$\times$ \\
\bottomrule
\end{tabular}
\end{table}

\emph{Full 38-match statistics (for reference only --- subset of 20 used in experiments):}

\begin{table}[H]
\centering
\small
\begin{tabular}{lr}
\toprule
\textbf{Statistic} & \textbf{38-match total} \\
\midrule
Total stroke records & 32,203 \\
Extracted frames & 216,112 JPEG \\
Unique players & 26 \\
Tournaments covered & 13 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Shot type distribution (N=32,203, full 38-match reference):}

\begin{table}[H]
\centering
\caption{ShuttleSet shot type distribution}
\small
\begin{tabular}{llrr}
\toprule
\textbf{Shot type (English)} & \textbf{Chinese} & \textbf{Count} & \textbf{\%} \\
\midrule
Net Drop & \begin{CJK}{UTF8}{bsmi}放小球\end{CJK} & 5,562 & 17.3\% \\
Lift & \begin{CJK}{UTF8}{bsmi}挑球\end{CJK} & 4,756 & 14.8\% \\
Net Block & \begin{CJK}{UTF8}{bsmi}擋小球\end{CJK} & 3,267 & 10.1\% \\
Clear & \begin{CJK}{UTF8}{bsmi}長球\end{CJK} & 2,551 & 7.9\% \\
Push & \begin{CJK}{UTF8}{bsmi}推球\end{CJK} & 2,519 & 7.8\% \\
Smash & \begin{CJK}{UTF8}{bsmi}殺球\end{CJK} & 2,237 & 6.9\% \\
Slice & \begin{CJK}{UTF8}{bsmi}切球\end{CJK} & 1,879 & 5.8\% \\
Short Serve & \begin{CJK}{UTF8}{bsmi}發短球\end{CJK} & 1,722 & 5.3\% \\
Tap Smash & \begin{CJK}{UTF8}{bsmi}點扣\end{CJK} & 1,522 & 4.7\% \\
Unknown & \begin{CJK}{UTF8}{bsmi}未知球種\end{CJK} & 1,273 & 4.0\% \\
Cross-Net & \begin{CJK}{UTF8}{bsmi}勾球\end{CJK} & 1,209 & 3.8\% \\
Trans. Slice & \begin{CJK}{UTF8}{bsmi}過度切球\end{CJK} & 1,193 & 3.7\% \\
Drive & \begin{CJK}{UTF8}{bsmi}平球\end{CJK} & 630 & 2.0\% \\
Rush & \begin{CJK}{UTF8}{bsmi}撲球\end{CJK} & 453 & 1.4\% \\
BG Drive & \begin{CJK}{UTF8}{bsmi}後場抽平球\end{CJK} & 394 & 1.2\% \\
Long Serve & \begin{CJK}{UTF8}{bsmi}發長球\end{CJK} & 354 & 1.1\% \\
Def. Drive & \begin{CJK}{UTF8}{bsmi}防守回抽\end{CJK} & 354 & 1.1\% \\
Def. Lift & \begin{CJK}{UTF8}{bsmi}防守回挑\end{CJK} & 271 & 0.8\% \\
Half Smash & \begin{CJK}{UTF8}{bsmi}小平球\end{CJK} & 57 & 0.2\% \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Dataset Comparison}

\begin{table}[H]
\centering
\small
\begin{tabularx}{\textwidth}{lXX}
\toprule
\textbf{Property} & \textbf{FineBadminton} & \textbf{ShuttleSet} \\
\midrule
\textbf{Primary role} & Few-shot classification (labeled) & SSL pre-training (unlabeled) \\
\textbf{Strategy labels} & Yes --- 5-class per shot & No \\
\textbf{Shot type labels} & 12 classes & 19 classes (Chinese) \\
\textbf{Frames provided?} & Yes (JPEG, $\sim$20fps) & No --- download + extract \\
\textbf{Scale (shots)} & 414 annotated / 296 in training & $\sim$17,000 shots (20 matches extracted) \\
\textbf{Video variety} & 11 matches, 1 camera angle & 20 matches extracted (38 usable, 26 players) \\
\textbf{Skeleton storage} & Per-rally \texttt{.npy} $(2, T_{\text{full}}, 34)$ & Per-shot \texttt{.npy} $(2, 16, 34)$ \\
\textbf{Hitter ordering} & At dataset load time & At extraction time \\
\textbf{Class imbalance} & Moderate & Severe (98$\times$) \\
\bottomrule
\end{tabularx}
\end{table}

%----------------------------------------------------------------------
\section{Design Reasoning Archive}
\label{app:design}
%----------------------------------------------------------------------

This appendix documents key design decisions, trade-offs, and reasoning that
shaped the project's experimental design.

\subsection{Why Skeleton-Based (Paradigm 1) Over Vision-Based (Paradigm 2)}

There are two fundamentally different ways to approach tactical strategy
recognition:

\textbf{Paradigm 1 (skeleton-based, chosen):} Video frames $\to$ pose estimation
$\to$ skeleton coordinates $\to$ encoder (ST-GCN or Transformer) $\to$ embedding $\to$
ProtoNet. The model never sees pixels.

\textbf{Paradigm 2 (vision-based, not chosen):} Video frames $\to$ visual
encoder (ViT, ResNet, VideoMAE) $\to$ embedding $\to$ ProtoNet. The model sees
raw pixels and must learn everything from the image.

Key trade-offs:
\begin{itemize}
  \item \textbf{Data efficiency:} Paradigm 1 is far more data-efficient.
    Structured skeleton input + graph priors means the model learns from
    less data. With only 40 labeled rallies and $\sim$5K
    unlabeled shots, skeleton-based is the pragmatic choice.
  \item \textbf{Strategy signal alignment:} The strategy taxonomy (Table~\ref{tab:strategies}) is
    defined almost entirely in terms of skeletal and positional signals.
  \item \textbf{Research novelty:} Skeleton + few-shot + tactical strategy is
    novel. ViT applied to sports video is well-explored.
  \item \textbf{What skeletons miss:} Shuttle trajectory, racket angle, and visual context.
    These are acknowledged as limitations.
\end{itemize}

\subsection{Where BST Fits (and Where It Does Not)}

BST (Chang, 2025) is not a separate box in the pipeline. It is an
alternative answer to one question: ``what encoder sits in the middle?''

``BST-style'' means: take BST's architectural idea --- a Transformer that
processes skeleton joint sequences using self-attention instead of graph
convolutions --- and drop it into our pipeline with our input
(skeleton-only, no shuttle trajectory) and our training regime (SimCLR
pre-training $\to$ ProtoNet few-shot).

We are NOT running BST itself. BST the actual model takes skeleton +
shuttlecock trajectory, is fully supervised on stroke-type labels, and
solves a different task (stroke classification).

\subsection{How the Prototypical Network Works}

Phase B involves minimal learning. A Prototypical Network is barely a
``network'' --- it is a nearest-neighbor lookup in the embedding space that
Phase A created.

\textbf{The literal procedure:}

Step 1: Take the 32 support rallies. Run each shot through the frozen
Phase A encoder to get a 256-dim embedding. For each strategy class,
average all embeddings belonging to that class. These averages are the
5 ``prototypes.'' This is arithmetic mean. No gradient descent.

Step 2: Take a new query shot. Run it through the same encoder. Measure
Euclidean distance to each of the 5 prototypes. Assign to the nearest
one.

\textbf{Alternatives considered:}
\begin{itemize}
  \item \textbf{k-NN (k=3 or k=5):} Classify by majority vote of k nearest
    support examples. No centroid assumption. Included as ablation.
  \item \textbf{Matching Networks:} Attention-weighted distance to every support
    example. Handles irregular class shapes but adds complexity.
  \item \textbf{MAML:} Fine-tunes the entire encoder per episode. Too complex
    for the small support set.
  \item \textbf{Simple linear probe:} Logistic regression on frozen embeddings.
    Included as a representation quality check.
\end{itemize}

\subsection{Why Input Representation Comes Before Encoder Architecture}

The ablation axes must be ordered because earlier decisions affect later
comparisons. Input representation comes first because you need to decide
what data goes into the encoder before you can meaningfully compare which
encoder is best.

The correct logic:
\begin{enumerate}
  \item Fix the encoder (ST-GCN). Find the best input representation.
  \item Take the best input. Now compare encoders.
  \item Take the best (encoder + input). Now compare pre-training.
  \item Take the best (encoder + input + pre-training). Now compare few-shot methods.
  \item Run K-shot sensitivity on the final best configuration.
\end{enumerate}

\subsection{Why Enriched Node Features Matter}

The report originally specified only raw $(x, y)$ coordinates as
node features --- 2 features per joint per frame. This forces the encoder
to derive all tactical signals from position alone. But the strategy
taxonomy explicitly requires signals the model cannot efficiently learn
from coordinates:

\begin{itemize}
  \item \textbf{Velocity:} ``Quick forward lunge'' (intercept) vs. ``stationary''
    (passive). Trivial computation wasted as network capacity.
  \item \textbf{Court context:} ``Forward court position'' (intercept) vs. ``rear
    court position'' (defensive). dist\_to\_net makes this explicit.
  \item \textbf{Body configuration:} ``Stretched posture'' (defensive) vs. ``neutral
    posture'' (passive). Joint angles encode this directly.
  \item \textbf{Inter-player relationship:} ``Opponent pushed back'' (create depth).
    dist\_to\_opponent\_centroid makes this a single feature.
\end{itemize}

\subsection{Shot Segmentation Design}
\label{app:windowing}

Each sample is a $T=16$ frame window centred on the hit frame ($\pm 8$ at 20fps $\approx 0.8$~s).

\textbf{Why frames BEFORE the hit are critical:} Tactical strategy is committed to during preparation, not at contact:
\begin{itemize}
  \item \textbf{Footwork direction:} A player moving to the net before striking reveals
    ``move to net'' strategy in their approach, not in the swing.
  \item \textbf{Preparation pose:} Shoulder/racket windup angle signals whether the
    decision was deliberate.
  \item \textbf{Opponent positioning:} Where the opponent is \emph{before} contact determines
    which strategy is rational.
\end{itemize}

\textbf{Why frames AFTER the hit are also included:} Post-contact frames confirm whether the executed shot matches the strategy.

\textbf{Dynamic role assignment per stroke:}

\begin{table}[H]
\centering
\small
\begin{tabular}{llllll}
\toprule
\textbf{Stroke} & \textbf{Hit frame} & \textbf{Hitter} & \textbf{Nodes 0--16} & \textbf{Nodes 17--33} \\
\midrule
Stroke 1 & Frame 10 & Player A & Player A skeleton & Player B skeleton \\
Stroke 2 & Frame 24 & Player B & Player B skeleton & Player A skeleton \\
Stroke 3 & Frame 38 & Player A & Player A skeleton & Player B skeleton \\
\bottomrule
\end{tabular}
\end{table}

Frame overlap between samples is intentional and correct --- consecutive strokes produce overlapping windows with different labels and different hitter assignments, so the overlap does not inflate metrics.

\end{document}